### 2023-10-04 3.Design/lstm.tex
changed serial vs par

This serial system has great advantages but comes with a few down sides. If the system we are working with has $n_h$ hidden states. This number of hidden states ($n_h$) is the major changing element in the final system(TODO ref final onchip area).

TODO : Rework
\begin{itemize}
  \item When the system is serialized, the inference time increases with a factor of $O(n_h)$.
  \item When the system is in parallel, the pointwise circuit's onChip area increases with a factor of $O(n_h^2)$.
    This is due to the fact that the onChip area of the pointwise part of the circuit increases with a factor of $O(n_h)$ and the onChip area of a crossbar array increase with a factor of $O(n_h^2)$. So the final increase of onChip area is $O(n_h^2+n_h)=O(n_h^2)$.
\end{itemize}

However, in both cases, the overall onChip area of the crossbar arrays increases with a factor of $O(n_h^2)$. That means that using the parallel system won't increase the onChip area by a lot as $n_h$ rises, because the $O(n_h)$ factor of the parallel version is absorbed as $O(n_h^2+n_h)=O(n_h^2)$.

That leads to the conclusion that the best thing to do is use an hybrid system (both serialized and parallel), using the limiting inference time for our system to set the maximum serial size. Depending on the system we're using this circuit for, we might have different time requirements.

>>>>

There is a sweet spot for the serial size ($n_s$) :

\begin{itemize}
  \item When the serial size ($n_s)$ increases, the inference time increases with a factor of $O(n_s)$ while the onChip area decrease with the same factor.
  \item When the serial size ($n_s)$ decreases, similarly, the onChip area increases with a factor of $O(n_s)$ while the tinference time decreases by the same factor.
\end{itemize}

The overall onChip area is linked to the number of hidden states ($n_h$) by $O(n_h^2)$. This means that the serial size ($n_s$) will be set depending on the limiting factor of our system (onChip area or inference time).
